Demo arXiv template

### 2022-10-11 paper/paper.qmd
A draft on why people should care about indices in intro

* indices, why do we need them, decision making
* define what is an index, what is not even if they are called index
* only very brief on indices in the introduction
* potential audience + what do you think they should learn from this work.

@@

  - decision making: need to consider multi-facet for allocating resources, [...]
  - to include or constructed to quantify a concept of interest: some papers on constructing tourism based climate indices etc

Integrate multiple information to produce a single number summary (across time).

@@

Indices quantify a concept of interest with no direct measure across time.
The concept of interest doesn't have direct measure can because it is impractical to measure the concept of interest at the population level. 
For example, it would be nearly impossible to include all the available stocks in the market to characterise stock market behavior, indices like Dow Jones Industrial Average, S&P 500, and Nasdaq Composite select a representative set of stocks to measure the overall market behavior. 
Also belong to this category is the economic indices like Consumer Price Index, where price changes of a basket of items are weighted to measure inflation. 
The lack of direct measure could also due to the absence of a universal definition on the concept of interest. 
Many natural and social concepts are fundamentally multi-facets and some indices combines measures from different domains to characterise the concept of interest. 
This includes drought indices constructed from meteorological, agricultural, hydrological, and social-economic variables [give some names?]. 
Social development indices like Human Development Index [ref] and Global Liveability Index [ref] measure various aspects on the quality of human capital and urban life.

@@

reusable

>>>>

\newpage

@@

Quantities that can't be directly measured is ubiquitous in our society and they can often be relevant for policy making, resource allocation, early prevention and operational purpose.
For example, fire authority would be interested to quantify fire risk since bushfire can have a huge impact on monetary loss, health, and local ecosystem among others.
Climatologists would be interested in monitoring the change in global condition since variability in atmospheric and oceanic condition has a direct impact on the global weather and climate.
Usually more than one variable is related to the concept of interest and they often needs to be integrated to make decisions.
<!-- From a modelling perspective, these unobserved quantities are called latent variables and existing methods can incorporate these latent variables in the model structure.  -->
A commonly used approach here is to construct an index with the observable variables.
This allows analysts to compare the quantity of interest across countries and also cross time.

<!--   - decision making: need to consider multi-facet for allocating resources, [...] -->
<!--   - to include or constructed to quantify a concept of interest: some papers on constructing tourism based climate indices etc -->

<!-- Integrate multiple information to produce a single number summary (across time). -->

@@

The meaning of indices varies across disciplines and in this article, an index is defined as a tool to quantify a concept of interest that does not have direct measure.
The concept of interest doesn't have direct measure can because it is impractical to measure the concept of interest at the population level. 
For example, it would be nearly impossible to include all the available stocks in the market to characterise stock market behavior, indices like Dow Jones Industrial Average, S&P 500, and Nasdaq Composite select a representative set of stocks to measure the overall market behavior. 
Also belong to this category is the economic indices like Consumer Price Index, where price changes of a basket of items are weighted to measure inflation. 
The lack of direct measure could also due to the absence of a universal definition on the concept of interest. 
Many natural and social concepts are fundamentally multi-facets and some indices combines measures from different domains to characterise the concept of interest. 
This includes drought indices constructed from meteorological, agricultural, hydrological, and social-economic variables [give some names?]. 
Social development indices like Human Development Index [ref] and Global Liveability Index [ref] measure various aspects on the quality of human capital and urban life.

@@

Here we assume a concept of interest is determined, relevant variables/ indicators are identified and available to construct indices.

### 2022-10-11 paper/paper.tex
A draft on why people should care about indices in intro

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners, breakable, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

\begin{itemize}
\tightlist
\item
  indices, why do we need them, decision making
\item
  define what is an index, what is not even if they are called index
\item
  only very brief on indices in the introduction
\item
  potential audience + what do you think they should learn from this
  work.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  decision making: need to consider multi-facet for allocating
  resources, {[}\ldots{]}
\item
  to include or constructed to quantify a concept of interest
\end{itemize}

Integrate multiple information to produce a single number summary
(across time).

@@

Indices quantify a concept of interest with no direct measure across
time. The concept of interest doesn't have direct measure can because it
is impractical to measure the concept of interest at the population
level. For example, it would be nearly impossible to include all the
available stocks in the market to characterise stock market behavior,
indices like Dow Jones Industrial Average, S\&P 500, and Nasdaq
Composite select a representative set of stocks to measure the overall
market behavior. Also belong to this category is the economic indices
like Consumer Price Index, where price changes of a basket of items are
weighted to measure inflation. The lack of direct measure could also due
to the absence of a universal definition on the concept of interest.
Many natural and social concepts are fundamentally multi-facets and some
indices combines measures from different domains to characterise the
concept of interest. This includes drought indices constructed from
meteorological, agricultural, hydrological, and social-economic
variables {[}give some names?{]}. Social development indices like Human
Development Index {[}ref{]} and Global Liveability Index {[}ref{]}
measure various aspects on the quality of human capital and urban life.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, enhanced, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi

\newpage

@@

Quantities that can't be directly measured is ubiquitous in our society
and they can often be relevant for policy making, resource allocation,
early prevention and operational purpose. For example, fire authority
would be interested to quantify fire risk since bushfire can have a huge
impact on monetary loss, health, and local ecosystem among others.
Climatologists would be interested in monitoring the change in global
condition since variability in atmospheric and oceanic condition has a
direct impact on the global weather and climate. Usually more than one
variable is related to the concept of interest and they often needs to
be integrated to make decisions. A commonly used approach here is to
construct an index with the observable variables. This allows analysts
to compare the quantity of interest across countries and also cross
time.

@@

The meaning of indices varies across disciplines and in this article, an
index is defined as a tool to quantify a concept of interest that does
not have direct measure. The concept of interest doesn't have direct
measure can because it is impractical to measure the concept of interest
at the population level. For example, it would be nearly impossible to
include all the available stocks in the market to characterise stock
market behavior, indices like Dow Jones Industrial Average, S\&P 500,
and Nasdaq Composite select a representative set of stocks to measure
the overall market behavior. Also belong to this category is the
economic indices like Consumer Price Index, where price changes of a
basket of items are weighted to measure inflation. The lack of direct
measure could also due to the absence of a universal definition on the
concept of interest. Many natural and social concepts are fundamentally
multi-facets and some indices combines measures from different domains
to characterise the concept of interest. This includes drought indices
constructed from meteorological, agricultural, hydrological, and
social-economic variables {[}give some names?{]}. Social development
indices like Human Development Index {[}ref{]} and Global Liveability
Index {[}ref{]} measure various aspects on the quality of human capital
and urban life.
